---
title: "Simulating the Central Limit Theorem"
author: "Emily Quinn Finney"
date: "December 21, 2016"
output: pdf_document
---

\section*{Overview}

In a few (2-3) sentences explain what is going to be reported on.

\section*{Simulations}
Include English explanations of the simulations you ran, with the accompanying R code. Your explanations should make clear what the R code accomplishes.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
mns = NULL
for (i in 1:1000) mns=c(mns, mean(rexp(40,0.2)))
```

\section*{Sample Mean versus Theoretical Mean}
Include figures with titles. In the figures, highlight the means you are comparing. - - Include text that explains the figures and what is shown on them, and provides appropriate numbers.

```{r}
mean(mns)
```

\section*{Sample Variance versus Theoretical Variance}
Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances.

```{r}
var(mns)
```

\section*{Distribution}
Via figures and text, explain how one can tell the distribution is approximately normal.

```{r}
hist(mns)
hist(rexp(40000,0.2))
```

Focus on the difference between the distribution of a large collection of random exponentials and the distribution of a large collection of averages of 40 exponentials.